The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
more figure 1 comments

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{How does this figure look if you show the plot range with the
  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
  might be nicer to do that and put a vertical line at $z=0.3$ to
  remind the reader that you only fit above that redshift.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}
